---
title: "CoefPlots of ParallelTrendsTest"
author: "Peng Sun"
date: "10/03/2022"
output: html_document
---
#Load packages
```{r load packages, message=FALSE, warning=FALSE}
#install.packages("clubSandwich")
library(readr)
library(did)
library(fixest)
library(DRDID)
library(tidyverse)
library(plm)
library(stargazer)
library(sandwich)
library(lmtest)
library(jtools)
library(clubSandwich)
```


#read data
```{r}
setwd("~/R")
df2012<-read_csv("~/R/df2012_20210920.csv")
```


```{r}
# set levels of timedummy variables so that Y2012 will be used as 
names(df2012)
unique(df2012$timedummy)
```


```{r}
df2012$timedummy<-fct_relevel(df2012$timedummy,levels="Y2012","Y2013","Y2014","Y2015","Y2016","Y2017","janapr18","t1","t2")
#set levels of groups dummies so that Group C will be used as base
df2012$groups<-fct_relevel(df2012$groups, levels="C","A","B","D")
# set levels of period dummies so that t0 period will be used as base
df2012$periods<-fct_relevel(df2012$periods, levels="t0","t1","t2")
df2012<-df2012%>%select(-1)


```



```{r}
df2012<-df2012 %>%
   mutate(timedummy2=case_when(year==2012~"Y2012",
                            year==2013~"Y2013",
                            year==2014~"Y2014",
                            year==2015~"Y2015",
                            year==2016~"Y2016",
                            year==2017~"Y2017",
                          janapr18==1~"Y2018janapr",
                            t1==1~"Yt1",
                            t2==1~"Yt2"))
df2012<- df2012%>% 
  mutate(timedummy3=as.factor(yearqrt))
class(df2012$timedummy3)
unique(df2012$timedummy3)
unique(df2012$timedummy2)
df2012<-df2012%>%
  mutate(timedummy6= case_when(timedummy3=="2012 Q1"~ "Y2012Q1",
                             timedummy3=="2012 Q2"~ "Y2012Q2",
                             timedummy3=="2012 Q3"~ "Y2012Q3",
                             timedummy3=="2012 Q4"~ "Y2012Q4",
                             timedummy3=="2013 Q1"~ "Y2013Q1",
                             timedummy3=="2013 Q2"~ "Y2013Q2",
                             timedummy3=="2013 Q3"~ "Y2013Q3",
                             timedummy3=="2013 Q4"~ "Y2013Q4",
                             timedummy3=="2014 Q1"~ "Y2014Q1",
                             timedummy3=="2014 Q2"~ "Y2014Q2",
                             timedummy3=="2014 Q3"~ "Y2014Q3",
                             timedummy3=="2014 Q4"~ "Y2014Q4",
                             timedummy3=="2015 Q1"~ "Y2015Q1",
                             timedummy3=="2015 Q2"~ "Y2015Q2",
                             timedummy3=="2015 Q3"~ "Y2015Q3",
                             timedummy3=="2015 Q4"~ "Y2015Q4",
                             timedummy3=="2016 Q1"~ "Y2016Q1",
                             timedummy3=="2016 Q2"~ "Y2016Q2",
                             timedummy3=="2016 Q3"~ "Y2016Q3",
                             timedummy3=="2016 Q4"~ "Y2016Q4",
                             timedummy3=="2017 Q1"~ "Y2017Q1",
                             timedummy3=="2017 Q2"~ "Y2017Q2",
                             timedummy3=="2017 Q3"~ "Y2017Q3",
                             timedummy3=="2017 Q4"~ "Y2017Q4",
                             janapr18==1~"Y2018janapr",
                             t1==1~"Yt2",
                             t2==1~"Yt3"
                             ))
unique(df2012$timedummy6)
df2012$timedummy6<-fct_relevel(df2012$timedummy6, levels="Y2012Q1","Y2012Q2","Y2012Q3","Y2012Q4","Y2013Q1","Y2013Q2","Y2013Q3","Y2013Q4","Y2014Q1","Y2014Q2","Y2014Q3","Y2014Q4","Y2015Q1","Y2015Q2","Y2015Q3","Y2015Q4","Y2016Q1","Y2016Q2","Y2016Q3","Y2016Q4","Y2017Q1","Y2017Q2","Y2017Q3","Y2017Q4","Y2018janapr","Yt2","Yt3")
```
```{r}
mean(df2012$land_area, na.rm="true")
```
```{r}
mean(df2012$floor_area)
# only keep three significant figures
```

```{r}
df2012_mutated <-  df2012  
df2012_mutated$contour=replace_na(df2012_mutated$contour,"Unreported") 
df2012_mutated$deck=replace_na(df2012_mutated$deck,"Unreported")   
df2012_mutated$roof_material=replace_na(df2012_mutated$roof_material,"Unreported") 
df2012_mutated$wall_material=replace_na(df2012_mutated$wall_material,"Unreported") 
df2012_mutated$building_age=replace_na(df2012_mutated$building_age,"Unreported")
df2012_mutated$land_area=replace_na(df2012_mutated$land_area,0.069) 
df2012_mutated$floor_area=replace_na(df2012_mutated$floor_area,136) 

# use a mean for land_area and floor_are
```
```{r}
#df2012_mutated$garages_mainroof=replace_na(df2012_mutated$garages_mainroof,"Unreported") 
```
```{r}
#head(garage)
```


```{r}
garage=df2012_mutated$garages_mainroof
```

```{r}
# replace msising values with Unreported
garage[is.na(garage)]<-"Unreported"
```

```{r}
which(is.na(garage))
```
```{r}
df2012_mutated$garages_mainroof<-garage
```

#Get the same obs for the pooled cross section models(fix the 30 obs difference)
```{r}
bedrooms_min=df2012_mutated$bedrooms_min
# replace msising values with Unreported
bedrooms_min[is.na(bedrooms_min)]<-"Unreported"
#head(bedrooms_min)
df2012_mutated$bedrooms_min<- bedrooms_min
```


```{r}
#write.csv(df2012, "chapter1_df2012.csv")
```
```{r}
#write.csv(df2012_mutated, "chapter1_df2012mutated_bedrooms.csv")
```
# Replication of Table 6 results
## Replication of Table 6 results_column 1
```{r}
plm_1<-plm(lp~t1+t2+A+B+D+t1*A+t2*A+t1*B+t2*B+t1*D+t2*D,data=df2012, model="pooling", index=c("houseid","year") )
summary(plm_1)
```


```{r}
coefplot(plm_1,keep=c("t1:A","t2:A","t1:B","t2:B","t1:D","t2:D"), ylim=c(-0.4,0.4), axis.text.x = element_text(size=14))
```


## Replication of Table 6 results_Column 2 (same obs # with Col 1, 3 and 5)
```{r}

lm_housefeature2<-lm(lp~t1+t2+t1*A+t2*A+t1*B+t2*B+t1*D+t2*D+floor_area+land_area+bedrooms_min+as.factor(building_age)+ as.factor(deck)+ as.factor(wall_material) 
+as.factor(roof_material)+as.factor(garages_mainroof)+ as.factor(contour)+as.factor(timedummy2) +as.factor(suburb),data=df2012_mutated)
summary(lm_housefeature2)
```


```{r}
coefplot(lm_housefeature2,keep=c("t1:A","t2:A","t1:B","t2:B","t1:D","t2:D"), ylim=c(-0.4,0.4), axis.text.x = element_text(size=14))
```

#Replication of Table 6 results_Column 3 



```{r}
plm_year<-plm(lp~yr2012+yr2013+yr2014+yr2015+yr2016+yr2017+t1+t2+A+B+D+t1*A+t2*A+t1*B+t2*B+t1*D+t2*D,data=df2012, model="within",effect="individual", index=c("houseid","year"))
summary(plm_year)
```

```{r}
coefplot(plm_year,keep=c("t1:A","t2:A","t1:B","t2:B","t1:D","t2:D"), ylim=c(-0.4,0.4), axis.text.x = element_text(size=14))
```

```{r}

#plm_year_coef<-coef_test(plm_year, vcov="CR2", cluster=df2012$houseid, test="Satterthwaite")

```


# Replication of Table 6 results_Column 4 (same obs# with Col 1, 3,5)
```{r}
housefeature_pretrends<-plm(lp~yr2012+yr2013+yr2014+yr2015+yr2016+yr2017+yr2012*A+yr2013*A+yr2014*A+yr2015*A+yr2016*A+yr2017*A+yr2012*B+yr2013*B+yr2014*B+yr2015*B+yr2016*B+yr2017*B+yr2012*D+yr2013*D+yr2014*D+yr2015*D+yr2016*D+yr2017*D+t1+t2+A+B+D+t1*A+t2*A+t1*B+t2*B+t1*D+t2*D+floor_area+land_area+bedrooms_min+as.factor(building_age)+ as.factor(deck)+ as.factor(wall_material) 
+as.factor(roof_material)+as.factor(garages_mainroof)+ as.factor(contour)+as.factor(suburb),data=df2012_mutated,model="pooling", index=c("houseid","year"))
summary(housefeature_pretrends)
```



#coef graph of Column 4
```{r}
coefplot(housefeature_pretrends,ylim=c(-0.4,0.4), keep=c("yr2012:A","yr2013:A","yr2014:A","yr2015:A","yr2016:A","yr2017:A","A:t1", "A:t2"), axis.text.x = element_text(size=14))
```

```{r}
coefplot(housefeature_pretrends,keep=c("yr2012:B","yr2013:B","yr2014:B","yr2015:B","yr2016:B","yr2017:B", "B:t1","B:t2"), axis.text.x = element_text(size=14))
```
```{r}
coefplot(housefeature_pretrends, keep=c("yr2012:D","yr2013:D","yr2014:D","yr2015:D","yr2016:D","yr2017:D", "D:t1", "D:t2"), axis.text.x = element_text(size=14))
```




## Replication of Table 6_Column 5, pretrends controlled, with 2018JanApr and C as baseline
```{r}
plm_year_house_parallel2018<-plm(lp~yr2012+yr2013+yr2014+yr2015+yr2016+yr2017+yr2012*A+yr2013*A+yr2014*A+yr2015*A+yr2016*A+yr2017*A+yr2012*B+yr2013*B+yr2014*B+yr2015*B+yr2016*B+yr2017*B+yr2012*D+yr2013*D+yr2014*D+yr2015*D+yr2016*D+yr2017*D+t1+t2+A+B+D+t1*A+t2*A+t1*B+t2*B+t1*D+t2*D,data=df2012, model="within",effect="individual", index=c("houseid","year"))
summary(plm_year_house_parallel2018)
```



#Coef graph of column 5

```{r}
coefplot(plm_year_house_parallel2018, ylim=c(-0.4,0.4),keep=c("yr2012:A","yr2013:A","yr2014:A","yr2015:A","yr2016:A","yr2017:A","janapr18:A"), axis.text.x = element_text(size=14))
```
# Robustness Check using Group D as the base group
## Robustness Check using Group D as the base group of Table 6 column 1
```{r}
plm_1D<-plm(lp~t1+t2+A+B+C+t1*A+t2*A+t1*B+t2*B+t1*D+t2*C,data=df2012, model="pooling", index=c("houseid","year") )
summary(plm_1D)
```


```{r}
coefplot(plm_1D,keep=c("t1:A","t2:A","t1:B","t2:B","t1:C","t2:C"), ylim=c(-0.4,0.4), axis.text.x = element_text(size=14))
```



## Robustness Check using Group D as the base group of Table 6 column2 (same obs # with Col 1, 3 and 5)
```{r}

lm_housefeature2D<-lm(lp~t1+t2+t1*A+t2*A+t1*B+t2*B+t1*C+t2*C+floor_area+land_area+bedrooms_min+as.factor(building_age)+ as.factor(deck)+ as.factor(wall_material) 
+as.factor(roof_material)+as.factor(garages_mainroof)+ as.factor(contour)+as.factor(timedummy2) +as.factor(suburb),data=df2012_mutated)
summary(lm_housefeature2D)
```


```{r}
coefplot(lm_housefeature2D,keep=c("t1:A","t2:A","t1:B","t2:B","t1:D","t2:D"), ylim=c(-0.4,0.4), axis.text.x = element_text(size=14))
```


## Robustness Check using Group D as the base group of Table 6 column 3 



```{r}
plm_yearD<-plm(lp~yr2012+yr2013+yr2014+yr2015+yr2016+yr2017+t1+t2+A+B+D+t1*A+t2*A+t1*B+t2*B+t1*C+t2*C,data=df2012, model="within",effect="individual", index=c("houseid","year"))
summary(plm_yearD)
```

```{r}
coefplot(plm_yearD,keep=c("t1:A","t2:A","t1:B","t2:B","t1:C","t2:C"), ylim=c(-0.4,0.4), axis.text.x = element_text(size=14))
```

 

## Robustness Check using Group D as the base group of Table 6 column4 (same obs# with Col 1, 3,5)
```{r}
housefeature_pretrendsD<-plm(lp~yr2012+yr2013+yr2014+yr2015+yr2016+yr2017+yr2012*A+yr2013*A+yr2014*A+yr2015*A+yr2016*A+yr2017*A+yr2012*B+yr2013*B+yr2014*B+yr2015*B+yr2016*B+yr2017*B+yr2012*C+yr2013*C+yr2014*C+yr2015*C+yr2016*C+yr2017*C+t1+t2+A+B+D+t1*A+t2*A+t1*B+t2*B+t1*C+t2*C+floor_area+land_area+bedrooms_min+as.factor(building_age)+ as.factor(deck)+ as.factor(wall_material) 
+as.factor(roof_material)+as.factor(garages_mainroof)+ as.factor(contour)+as.factor(suburb),data=df2012_mutated,model="pooling", index=c("houseid","year"))
summary(housefeature_pretrendsD)
```



```{r}
coefplot(housefeature_pretrendsD,ylim=c(-0.4,0.4), keep=c("yr2012:A","yr2013:A","yr2014:A","yr2015:A","yr2016:A","yr2017:A","A:t1", "A:t2"), axis.text.x = element_text(size=14))
```

```{r}
coefplot(housefeature_pretrendsD,keep=c("yr2012:B","yr2013:B","yr2014:B","yr2015:B","yr2016:B","yr2017:B", "B:t1","B:t2"), axis.text.x = element_text(size=14))
```
```{r}
coefplot(housefeature_pretrendsD, keep=c("yr2012:C","yr2013:C","yr2014:C","yr2015:C","yr2016:C","yr2017:C", "C:t1", "C:t2"), axis.text.x = element_text(size=14))
```

## Robustness Check using Group D as the base group of Table 6 column 5, pretrends controlled, with 2018JanApr and C as baseline
```{r}
plm_year_house_parallel2018D<-plm(lp~yr2012+yr2013+yr2014+yr2015+yr2016+yr2017+yr2012*A+yr2013*A+yr2014*A+yr2015*A+yr2016*A+yr2017*A+yr2012*B+yr2013*B+yr2014*B+yr2015*B+yr2016*B+yr2017*B+yr2012*C+yr2013*C+yr2014*C+yr2015*C+yr2016*C+yr2017*C+t1+t2+A+B+D+t1*A+t2*A+t1*B+t2*B+t1*C+t2*C,data=df2012, model="within",effect="individual", index=c("houseid","year"))
summary(plm_year_house_parallel2018D)
```


```{r}
coefplot(plm_year_house_parallel2018, ylim=c(-0.4,0.4),keep=c("yr2012:A","yr2013:A","yr2014:A","yr2015:A","yr2016:A","yr2017:A","janapr18:A"), axis.text.x = element_text(size=14))
```

```{r}
coefplot(plm_year_house_parallel2018D,keep=c("yr2012:B","yr2013:B","yr2014:B","yr2015:B","yr2016:B","yr2017:B"), axis.text.x = element_text(size=14))
```

```{r}
coefplot(plm_year_house_parallel2018D, keep=c("yr2012:C","yr2013:C","yr2014:C","yr2015:C","yr2016:C","yr2017:C"), axis.text.x = element_text(size=14))
```

# Robustness check by dropping houses with less than two bedrooms
```{r}
df2012_2beds<-  df2012 %>% filter(bedrooms_min<=1|bedrooms_min =="NA")
dim(df2012_2beds)
```

```{r}
df2012_2morebeds<-  df2012 %>% filter(bedrooms_min>=1|bedrooms_min !="NA")
dim(df2012_2morebeds)
```